---
title: "Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
```

## Linear Regression Package
This is a R package of implementing Linear Regression with the methods below: 
:print
:plot
:pred
:coef
:resid
:summary

The package uses S3 object orientation to implement the above mentioned methods. An object is created by defining a formula that defines a relationship between a dependent variable and the other independent variables, and defining a dataset where the values of these variables are contained (example below). The above mentioned methods can then be used on this object, the methods are discussed below. 


## Let's start

1. Download the package "devtools::install_github ("bh1995/luckylab2.0/linreg")

2. The function called
linreg() and have the two arguments "formula" and "data", e.g. formula =Petal.Length~Species, data = iris

3. Then store the function into a variable(e.g. regmodel <- linreg(formula, data) )

4. It will be what it looks like:

## print(regmodel)
```
```
## plot(regmodel)
```
```
## pred(regmodel)
```
```
## coef(regmodel)
```
```
## resid(regmodel)
```
```
## summary(regmodel)
```
```



