---
title: "Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
```

## Linear Regression Package
This is a R package of implementing Linear Regression with the methods below: 
<br /> 

*
print
<br /> 

*
plot
<br />

*
pred
<br />

*
coef
<br />

*
resid
<br />

*
summary

The package uses S3 object orientation to implement the above mentioned methods. An object is created by defining a formula that defines a relationship between a dependent variable and the other independent variables, and defining a dataset where the values of these variables are contained (example below). The above mentioned methods can then be used on this object, the methods are discussed below. 



## Let's start

1. Download the package "devtools::install_github ("bh1995/luckylab2.0/linreg", build_vignettes = TRUE)

2. The function called
`<linreg()>` and have the two arguments *"formula"* and *"data"*, e.g. `< formula = Petal.Length~Species>`,`<data(iris) >`

3. Then store the function into a variable(e.g. `<regmodel <- linreg(formula, iris)>` )

4. It will be look like:

```{r, include = TRUE}
# example object named "test" created using the iris dataset.

test <- linreg(formula = Petal.Length~Sepal.Width+Sepal.Length, data = iris)

```
## print
The print method will print the coefficients of the solution as shown below.

```{r, include = TRUE}
# example of using the print method on the object test.

print(test)

```

## plot
Using the plot method two plots will be created. One of residuals vs the fitted values and one plot of the scaled residuals vs fitted values.
```{r, include=TRUE}
# example of the plot method using test.
plot(test)

```

## pred
The pred method will return the the predicted values of the dependent variable.
```{r, include = TRUE}
# example of the pred method using test.
head(pred(test))

```

## coef
Using the coef method returns the coeficients of the given object.
```{r, include = TRUE}
# example of the coef method using test.
coef(test)

```

## resid
Using resid, the vector of residuals will be returned.
```{r, include = TRUE}
# example of the coef method using test.
head(resid(test))

```

## summary
The summary method will return the coeficients, their standard error, t-values and p-values, the estimated residual variance and the degrees of freedom.
```{r, include = TRUE}
# example of summary using test.
summary(test)

```


